Vegetation regrowth/encroachment (gjengroing)

### 2023-08-30 gjengroing.Rmd
Alter the gjengroing chapter to display images correctly AND Re-render

---
title: "Vegetation regrowth/encroachment (gjengroing)"
output:
  pdf_document: default
  html_document: default
---

@@

```{r}
include_graphics('/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/gjengroing/R_project/DATA/images/val_1.jpg')
```

@@

```{r}
include_graphics('/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/gjengroing/R_project/DATA/images/val_2.jpg')
```

@@

```{r}
include_graphics('/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/gjengroing/R_project/DATA/images/val_3.jpg')
```

@@

```{r}
include_graphics('/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/gjengroing/R_project/DATA/images/val_4.jpg')
```

@@

```{r}
include_graphics('/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/gjengroing/R_project/DATA/images/val_5.jpg')
```

>>>>

# Vegetation regrowth/encroachment (gjengroing) {#gjengroing}

@@

![](images/val_1.jpg)

@@

![](images/val_2.jpg)

@@

![](images/val_3.jpg)

@@

![](images/val_4.jpg)

@@

![](images/val_5.jpg)
